### 2025-12-10 Paper/paper_2025.tex
Updates from Overleaf

    add outcome graphs

@@

>>>>

    \import{Objects}{hosp_outcomes_table.tex}

    \section{Estimating Anti-competitive Effects of Board Overlap}

    One of the biggest challenges to understanding

@@

    \appendix

% First part of the figure (page 1)
\begin{figure}[p] % 'p' places figure on a dedicated float page
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{bed_conc}
        \caption{Caption for image 1}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image2}
        \caption{Caption for image 2}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image3}
        \caption{Caption for image 3}
    \end{subfigure}

    \caption{Overall caption for stacked subfigures (part 1)}
\end{figure}

% Second part of the figure (page 2)
\begin{figure}[p]
    \ContinuedFloat % continues numbering from previous figure
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image4}
        \caption{Caption for image 4}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image5}
        \caption{Caption for image 5}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image6}
        \caption{Caption for image 6}
    \end{subfigure}

    \caption{Overall caption for stacked subfigures (part 2)}
\end{figure}

% Third part of the figure (page 3)
\begin{figure}[p]
    \ContinuedFloat
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image7}
        \caption{Caption for image 7}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image8}
        \caption{Caption for image 8}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{image9}
        \caption{Caption for image 9}
    \end{subfigure}

    \caption{Overall caption for stacked subfigures (part 3)}
\end{figure}
